---
title: "R Notebook"
output: html_notebook
---

```{r}
library(prob)
library(gtools)
library(tidyverse)
```

# 1. If I roll a six-sided dice once, what is the probability of getting a number less than 5?
# A. 5/6

# 2. How many outcomes are there in the sample space of an experiment in which we toss three dice?
# A. (6x6x6) = 216 

# 3. In an experiment where we roll four dice:
#Q. i. How many outcomes are in the event total_equals_5_6_7 (i.e. the total of the four dice equals 5, 6 or 7)?
A. 34
# what is the probability of this event?
A. 34/ 1296 = 0.02623
# what assumptions do we apply in answering part ii?
# That the die can be thrown in any order. 

# Q3 i
```{r}
s_four_dice <- rolldie(4)
view(s_four_dice)
```

# Q3 i
```{r}
s_sum_equals_five <- s_four_dice %>%
  filter(X1 + X2 + X3 + X4 == 5)
s_sum_equals_five
```

# Q3 i
```{r}
s_sum_equals_six <- s_four_dice %>%
  filter(X1 + X2 + X3 + X4 == 6)
s_sum_equals_six
```
# Q3 i
```{r}
s_sum_equals_seven <- s_four_dice %>%
  filter(X1 + X2 + X3 + X4 == 7)
s_sum_equals_seven
```

# 4. Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?



# 5. I roll six dice:
# what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?
# what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?




