---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

2.1 Load the data into a dataframe project
```{r}
project <- read_csv("data/project_management.csv")
```


```{r}
summary(project)
```

2.2 Plot the data, taking estimated_length as the independent variable and actual_length as the dependent variable.
```{r}
project_plot <- project %>%
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point()
 project_plot 
```

2.3 Label the data points with their row number in the data frame using geom_text()
2.3.1 Identify by eye any points you think might be outliers and note their labels. A. 5 Top right
2.3.2 Further split your outliers into those you think are ‘influential’ or ‘non-influential’ based on a visual assessment of their leverage. A.
```{r}
project_plot <- project %>%
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_text() +
  aes(label = 1:nrow(project)) +
  geom_point()
 project_plot
```

```{r}
model <- lm(formula = actual_length ~ estimated_length, data = project)

model
```


```{r}
project_plot <- project %>%
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_text() +
  aes(label = 1:nrow(project)) +
  geom_point() +
  plot(model)
 project_plot
```
















