---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(infer)
```

```{r}
clean_names <- read_csv("ames.csv")

```

```{r}
view(clean_names)
```

```{r}
glimpse(clean_names)
```

Q2. Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find? 
A. The distribution shows a high concentration around 25,000, with a considerable number of outliers, with 4 in the range of
```{r}
ggplot(clean_names) +
  aes(x = Lot.Area) +
  geom_histogram(bins = 25, col = "white")
```

```{r}
ggplot(clean_names) +
  aes(x = Lot.Area) +
  geom_boxplot()

```


```{r}
clean_names_stats <- clean_names %>%
  summarise(
    count = n(),
    mean = mean(Lot.Area),
    sd = sd(Lot.Area)
  )
clean_names_stats
```


Q3. Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses
```{r}
bootstrap_clean_names <- clean_names %>%
  rep_sample_n(size = 200, replace = TRUE, reps = 5000) %>%
  summarise(Lot.Area = mean(Lot.Area))
bootstrap_clean_names

```

```{r}
bootstrap_clean_names %>%
  ggplot(aes(x = Lot.Area)) +
  geom_histogram(col = "white") +
  labs(x = "Mean_Lot_Area")
```


Q4. Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution
```{r}
ci_95 <- bootstrap_clean_names %>%
  summarise(
    mean = mean(Lot.Area),
    lower_bound = quantile(Lot.Area, probs = 0.025),
    upper_bound = quantile(Lot.Area, probs = 0.975)
  )
ci_95

```


```{r}
infer_clean_names <- clean_names %>%
  specify(response = Lot.Area) %>%
  generate(reps = 5000, type = "bootstrap") %>%
  calculate(stat = "mean")

infer_clean_names
```

```{r}
infer_ci_95 <- infer_clean_names %>%
  get_ci(level = 0.95, type = "percentile")
infer_ci_95

```

```{r}
infer_clean_names %>%
  visualise() +
  shade_confidence_interval(endpoints = infer_ci_95)

```

Q5. You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95% CI? Does that make sense?
A. The graph is broader of the 99% is broader than the 95%. yes it makes sense as it is now 99% percentile of the total.
```{r}
infer_ci_99 <- infer_clean_names %>%
  get_ci(level = 0.99, type = "percentile")
infer_ci_99

```

 
```{r}
infer_clean_names %>%
  visualise() +
  shade_confidence_interval(endpoints = infer_ci_99)
```

Q6. Calculate the point estimate of the mean(lot_area)
```{r}
point_ests <- clean_names %>%
  rep_sample_n(size = 50, reps = 1) %>%
  ungroup() %>%
  summarise(
    mean_Lot.Area = mean(Lot.Area),
  )
point_ests


```


