---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

Question 1
```{r}
# load in data 
code_clan_tweets <- read_csv("code_clan_tweets.csv")
code_clan_tweets
```

```{r}
# Find the number of rows, columns, and list all the variable names
#Rows: 234. Columns:  27
dim(code_clan_tweets)
names(code_clan_tweets)
code_clan_tweets

```

```{r}
head(code_clan_tweets)
```
```{r}
view(code_clan_tweets)
```


Question 2. we’re going to summarise the number of likes (favorite_count) CodeClan tweets have. Create a boxplot to check for outliers.

```{r}
code_clan_tweets_variables <- code_clan_tweets %>%
    select(favorite_count)

boxplot(code_clan_tweets_variables)

```

Question 3. Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).
```{r}
sum_code_clan_tweets <- summarise(code_clan_tweets, n = n())
sum_code_clan_tweets
```


Question 4. Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.
```{r}
summary(code_clan_tweets$retweet_count)

```

```{r}
unique(code_clan_tweets$source)

```

```{r}
code_clan_source <- code_clan_tweets %>%
  mutate()
  group_by("source"())
head(code_clan_source)

sum_tweets <- summarise(code_clan_source, n = n())
sum_tweets

```

Question 5. Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.
```{r}


```

Question 6. Find the mean number of characters that a CodeClan tweet contains.
```{r}

```


Question 7. The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.
```{r}

```


Question 8. From your new joined data, create a new tibble codeclan_hashtags containing only the tweet_id and hashtags in lowercase for analysis. Keep only those tweets with hashtags.
```{r}

```










