---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(cluster)
library(factoextra)
library(dendextend)
library(janitor)

```

Clustering

```{r}
mall_customers <- read_csv("mall_customers.csv")
```

```{r}
mall_customers
```

```{r}
head(mall_customers)

```

```{r}
summary(mall_customers)
```

```{r}
mall_customers_clean <- mall_customers %>%
  clean_names() %>%
  select(gender, age, annual_income_k, spending_score_1_100)
mall_customers_clean
```

1.You have been provided some customer data from a shopping centre. Do some exploratory analysis on the data. Comment on findings.
A. There appear to be 5 loose clusters on the graph below. With a clear concentration and cluster around the x-axis = 55 (annual_income_k) and y-axis = 50 (spending_score_1_1000 
```{r}
mall_customers_clean_plot <- mall_customers_clean %>%
  select(c(annual_income_k, spending_score_1_100))

ggplot(mall_customers_clean, aes(annual_income_k, spending_score_1_100)) +
  geom_point()
```

```{r}
mall_customers_clean_age <- mall_customers_clean %>%
  select(c(age, spending_score_1_100))

ggplot(mall_customers_clean, aes(age, spending_score_1_100)) +
  geom_point()
```


2.We are interested in creating a marketing campaign to target customers based on their spending score and annual income. Perform a k-means clustering to find if there are meaningful clusters in the data to target the customers.
A. Yes there are 5 clear identified clusters
```{r}
mall_customers_clean_scale <- mall_customers_clean %>% 
                      mutate_all(scale) 

summary(mall_customers_clean_scale)
```


3.Perform k-means clustering and chose a value of k.

```{r}
library(factoextra)
```

Each of the methods of choosing k:
3.1 Elbow method
A. From below I read 2 options k = 3 or k = 5. k = 5 looks to be clearer
```{r}
fviz_nbclust(mall_customers_clean_scale, kmeans, method = "wss", nstart = 25)
```

3.2 Silhouette coefficient
A. K = 5 is optimal here
```{r}
fviz_nbclust(mall_customers_clean_scale, kmeans, method = "silhouette", nstart = 25)
```

3.3 Gap statistic
A.  Result K = 1 
```{r}
fviz_nbclust(mall_customers_clean_scale, kmeans, method = "gap_stat")
```

A. From reading all of the above clusters K = 3 or K = 5 give optimal results. I'm going for k = 5


4.Visualise the clustering for your chosen value of k.
```{r}
library(animation)

mall_customers_clean_scale %>% 
  kmeans.ani(centers = 5)
```


5.Do you think the clustering seems a good fit for this data?
A. Yes I think the 5 clusters give a good clear fit for the data 


6.Comment on the attributes on one or two of the clusters (maybe even give them a label if you like - like in section 4.1 of the ‘Segmentation & clustering intro’ lesson).
While there are 5 clusters shown above plotting Annual income vs Spending score, it is clear form the graph factoring in age there highest spenders are all predominately under the age of 40 - presumably as the are likely to not have children and also have a higher disposable income.
6.1 The under 40 with high disposable income (top left)
6.2 The over 40 with low disposable income





