---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```


```{r}
kc_house <- read_csv("kc_house_data.csv")

```

```{r}
summary(kc_house)

```

```{r}
kc_house
```

1. Tidy up the data ready for regression:
1.1 You might like to think about removing some or all of date, id, sqft_living15, sqft_lot15 and zipcode (lat and long provide a better measure of location in any event).
```{r}
kc_house_clean <- kc_house %>%
  select(-c(date, id, sqft_living15, sqft_lot15, zipcode))
kc_house_clean 

```

1.2 Have a think about how to treat waterfront. Should we convert its type?
```{r}
houses_tidy_numeric <- kc_house_clean %>%
  select_if(is.numeric)
houses_tidy_numeric
```

```{r}
unique(kc_house_clean$waterfront)
```


1.3 We converted yr_renovated into a renovated logical variable, indicating whether the property had ever been renovated. You may wish to do the same.
```{r}


```

1.4 Have a think about how to treat condition and grade? Are they interval or categorical ordinal data types?
```{r}


```





















