---
title: "R Notebook"
output: html_notebook
---

# 1 Homework Info
```{r}
library(ggplot2)
library(CodeClanData)
library(tidyverse)
```

```{r}
backpack
```

# 2. MVP

# Question 1

```{r}
head(backpack)
dim(backpack)
names(dim(backpack))
glimpse(backpack)
slice_min(backpack, 10)
backpack
```

# Question 2. What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.
# A.there is a large grouping around, with a few outliers around 25, up to 1 at 35. 
```{r}
ggplot(backpack) +
  geom_bar(aes(x = backpack_weight, fill = ratio)) +
  scale_fill_brewer()
           
```

# Question 3. Are there differences in backpack weight between sex?
A. 
```{r}
ggplot(backpack) +
  geom_bar(aes(x = backpack_weight, fill =  sex), position = "dodge") +
  scale_fill_brewer()
```

# Question 4. What is the relationship between body weight and backpack weight?
```{r}
ggplot(backpack) +
  geom_bar(aes(x = backpack_weight, y = count, group = body_weight)) +
  scale_fill_brewer()

```

# Question 5. Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.
```{r}
ggplot(backpack) +
  geom_line(aes(x = backpack_weight, y = count, group = sex))

```

# Question 6. What proportion of students report back pain?
```{r}


```

# Question 7. Is this proportion different between men and women?
```{r}


```


# Question 8. Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.
```{r}


```







