---
title: "R Notebook"
output: html_notebook
---

```{r}
library(RPostgreSQL)
```

```{r}
home_location <- Sys.getenv("HOME")
credentials_location <- paste0(home_location,"/credentials.R")
source(credentials_location)

db_connect <- dbConnect(drv = PostgreSQL(), user = postgresql_username, password = postgresql_password, dbname = "acme_employees", host = "localhost")

rm(postgresql_username, postgresql_password)
```

```{r}
db_connect
```

```{r}
dbListTables(db_connect)
```

1. Create a new data.frame containing the details of all employees held in the database
```{sql connection=db_connect}
SELECT *
FROM employees
```

2. Retrieve the records for all employees again, but this time add a field full_name containing the first_name and last_name of each employee separated by a space.
```{sql connection=db_connect}
SELECT
  id,
  first_name,
  last_name,
  CONCAT(first_name, ' ', last_name)
FROM employees
```

3. Retrieve the details of all employees again, but this time listing their team name (as team_name), rather than their team_id.
```{sql connection=db_connect}
SELECT
  first_name,
  last_name,
  name
FROM employees
LEFT JOIN teams
ON employees.team_id = teams.id
```

```{sql connection=db_connect}
SELECT *
FROM teams
```

4. Do a breakdown of the number of employees per team (here we want two columns: team_name and num_employees). Order the table in decreasing number of employees. Include all teams, even if they have no employees.

```{sql connection=db_connect}
SELECT 
  teams.name AS team_name, 
  COUNT(employees.id) AS num_employees
FROM employees 
RIGHT JOIN teams
ON employees.team_id = teams.id
GROUP BY teams.name
ORDER BY num_employees DESC
```

5. AcmeCorp management want to send an email survey to each of their employees. However, they are worried that some of the employees may not receive the email either because their email addresses may be invalid (in that they don’t contain an ‘@’ symbol), or they may not have a stored email address at all. Can you find all these employees?

```{sql connection=db_connect}
SELECT
first_name,
  last_name,
  email
FROM employees
WHERE (email IS NULL) OR (email NOT LIKE '%@%')
```



