---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(cluster)
library(factoextra)
library(dendextend)
```


```{r}
computers <- read_csv("computers.csv")
```

```{r}
head(computers)
```

```{r}
summary(computers)
```

Clustering lab

1. Explore the data - do you think it looks potentially suitable for clustering?
A. Yes, the metrics above for hd and ram look to be good for clustering. Plus there are n/a in the data 

2. Chose a value of k

```{r}
computers_scale <- computers %>%
  janitor::clean_names() %>%
  select(c(hd, ram))
computers_scale 
```
```{r}
ggplot(computers_scale, aes(x = hd, y = ram)) +
    geom_point()
```

```{r}
computers_cluster<- kmeans(computers_scale, centers = 6, nstart = 25)
computers_cluster
```


3. Create clusters with chosen value of k - pull out the sizes of the clusters and the average of each variable in the dataset for each cluster.
```{r}
library(animation)
```

```{r}
library(broom)
```
```{r}
plot(computers_scale, cex = 0.5, hang = -5)
rect.hclust(computers_scale, k = 1, border = 2:5)
```

```{r}
max_k <- 20 

computer_clusters <- tibble(k = 1:max_k) %>%
  mutate(
    kclust = map(k, ~ kmeans(computers_scale, .x, nstart = 25)),
    tidies = map(kclust, tidy),
    glanced = map(kclust, glance),
augmented = map(kclust, augment, ram)
  )

computer_clusters
```

```{r}
computers_scale %>% 
  kmeans.ani(centers = 5) 
```

```{r}

```

4. Visualise the clusters.

```{r}
fviz_nbclust(computers_scale, kmeans, method = "silhouette", nstart = 25)
```

```{r}
fviz_nbclust(computers_scale, kmeans, method = "gap_stat", nstart = 25, k.max = 6)

```
``

```{r}
ggplot(computers_scale, aes(x = k, y = tot.withinss)) +
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks = seq(1,20, by = 11))
```



```{r}
computers_scale %>%
  filter(k <= 6) %>%
  ggplot(aes(x = hd, y = ram)) +
  geom_point(aes(colour = .cluster)) +
  facet_wrap(~k)
  
```


5. Comment on the results - do you think the clustering worked well?
? a number of errors and I cant see if its worked well!












