---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
starbucks_drink <- read.csv("starbucks_drinkMenu_expanded.csv")
starbucks_drink
```

Question 2 Load in the dataset and have a look at it.
```{r}
head(starbucks_drink)
dim(starbucks_drink)
names(dim(starbucks_drink))
glimpse(starbucks_drink)
starbucks_drink
```

Question 3. Investigate the calories of different drinks.
```{r}
starbucks_drink_calories <- select(starbucks_drink, 'Beverage_category', 'Beverage', 'Beverage_prep', 'Calories') %>%
        arrange(desc(Calories))
starbucks_drink_calories

```

```{r}
starbucks_drink_calories <- select(starbucks_drink, 'Beverage_category', 'Beverage', 'Beverage_prep', 'Calories') %>%
        drop_na(starbucks_drink_calories)
starbucks_drink_calories

```

Question 4 Create a new variable (column) called calorie_diff
```{r}
calorie_diff = mutate(starbucks_drink_calories, calorie_diff = Calories - 135  )
calorie_diff

```

Question 5 Summarise the mean number of calories in each beverage_category
```{r}
mean_calories <- summarise(starbucks_drink_calories) %>%
                          beverage_category = mean(Calories)
                          arrange(desc(Calories))
mean_calories
```

state_stats
Question 6 What is the average number of calories in each Beverage_prep type?
```{r}


```


Question 7 Which Beverage_prep type contains more than the average calories of all drinks?
```{r}


```

Question 8 Which is the best type of coffee drink to get if you’re worried about consuming too many calories?
```{r}


```


















