---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
```

```{r}
library(dplyr)
```


```{r}
salaries <- read_csv("salaries.csv")
```

```{r}
head(salaries)
```

```{r}
dim(salaries)
```


1 Using the dplyr verbs
Use the salaries dataset to answer the following questions.

1. Use select to see the beginning salary variable and the current salary variable
```{r}
salaries %>%
  select(beginning_salary,current_salary)
```

2. Use filter to see the employees aged over 50, who have a salary over £20,000.
```{r}
salaries %>%
  filter(age > 50.00, current_salary > 20000)
```

3. Use arrange to order by the data so that the highest salaries are first.

```{r}
arrange(salaries, desc(current_salary))
```

4. Use mutate to make a new variables beginning_salary_pence and current_salary_pence. These should have the corresponding salaries in pence instead of pounds.



```{r}
salaries_pp <- salaries %>%
  mutate(
    beginning_salary = str_c(beginning_salary_pence),
    current_salary = str_c(current_salary_pence)
  )
salaries_pp
```

5. Use summarise to find the maximum age and the minimum age.
```{r}
salaries %>%
  summarise(max(age))

```

```{r}
salaries %>%
  summarise(min(age))

```

6. Find the minimum salary and the maximum salary.

```{r}
salaries %>%
  summarise(max(current_salary))

```

```{r}
salaries %>%
  summarise(min(current_salary))

```

7. Find all the employees aged under 30.
```{r}
salaries %>%
  filter(age < 30)

```

8. Order the data in terms of increasing educational level where ties are broken using age.
```{r}

```



