---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
library(dplyr)
```

1.1 Load the diamonds.csv data set and undertake an initial exploration of the data. You will find a description of the meanings of the variables on the relevant Kaggle page
```{r}
diamonds <- read_csv("diamonds.csv")
diamonds
```

```{r}
summary(diamonds)
```

```{r}
library(ggiraphExtra)
library(GGally)
```

1.2 We expect the carat of the diamonds to be strong correlated with the physical dimensions x, y and z. Use ggpairs() to investigate correlations between these four variables.
```{r}
ggpairs(diamonds)
```

1.3 So, we do find significant correlations. Let’s drop columns x, y and z from the dataset, in preparation to use only carat going forward.

```{r}
diamonds_xyz <- diamonds %>%
  select(-x, -y, - z)
diamonds_xyz

```

1.4 We are interested in developing a regression model for the price of a diamond in terms of the possible predictor variables in the dataset.
i. Use ggpairs() to investigate correlations between price and the predictors (this may take a while to run, don’t worry, make coffee or something).
```{r}
ggpairs(diamonds_xyz)

```

1.4 i. Perform further ggplot visualisations of any significant correlations you find.
```{r}
diamonds_xyz %>%
  ggplot(aes(y = carat)) +
  geom_boxplot()
```

```{r}
plot_diamonds <- diamonds_xyz %>%
  ggplot(aes(x = color, y = carat)) +
  geom_point()
plot_diamonds
```

```{r}
plot_diamonds <- diamonds_xyz %>%
  ggplot(aes(x = price, y = carat)) +
  geom_point()
plot_diamonds
```

1.5 Shortly we may try a regression fit using one or more of the categorical predictors cut, clarity and color, so let’s investigate these predictors:
i. Investigate the factor levels of these predictors. How many dummy variables do you expect for each of them?
```{r}

```

```{r}
library(fastDummies)
```

Use the dummy_cols() function in the fastDummies package to generate dummies for these predictors and check the number of dummies in each case.
```{r}
diamonds_xyz_dummy <- diamonds_xyz %>%
  dummy_cols(select_columns = "carat", remove_first_dummy = TRUE, remove_selected_columns = TRUE)
diamonds_xyz_dummy
```










